Prefetching SPARQL query cacher

### 2016-05-13 dissertation/cache-proxy.tex
versions used for analysis
a bit about attean and traits

  \pmodule{AtteanX::Query::Cache} & Kjetil Kjernsmo, Gregory Todd Williams &
  \url{kjetilk/p5-atteanx-query-cache} \\

  \pmodule{AtteanX::Store::SPARQL} & Kjetil Kjernsmo &
  \url{kjetilk/p5-atteanx-store-sparql} \\

  \pmodule{AtteanX::Store::LDF} & Kjetil Kjernsmo, Patrick Hochstenbach &
  \url{phochste/AtteanX-Store-LDF} \\

  \pmodule{LWP::UserAgent::CHICaching} & Kjetil Kjernsmo &
  \url{kjetilk/p5-lwp-useragent-chicaching} \\

  \pmodule{Attean} & Gregory Todd Williams, Kjetil Kjernsmo &
  \url{kasei/attean} \\

  \pmodule{AtteanX::Endpoint} & Gregory Todd Williams &
  \url{kasei/atteanx-endpoint} \\

  \pmodule{RDF::LDF} &  Patrick Hochstenbach, Gregory Todd Williams, Jakob Voß,
  Kjetil Kjernsmo & \url{phochste/RDF-LDF} \\

@@

>>>>

  \pmodule{AtteanX::Query::Cache} & Kjetil Kjernsmo, Gregory Todd Williams &
  \url{kjetilk/p5-atteanx-query-cache} \\ % 0.001_04

  \pmodule{AtteanX::Store::SPARQL} & Kjetil Kjernsmo &
  \url{kjetilk/p5-atteanx-store-sparql} \\ % 0.008

  \pmodule{AtteanX::Store::LDF} & Kjetil Kjernsmo, Patrick Hochstenbach &
  \url{phochste/AtteanX-Store-LDF} \\ % 0.02

  \pmodule{LWP::UserAgent::CHICaching} & Kjetil Kjernsmo &
  \url{kjetilk/p5-lwp-useragent-chicaching} \\ % 0.04

  \pmodule{Attean} & Gregory Todd Williams, Kjetil Kjernsmo &
  \url{kasei/attean} \\ % 0.015

  \pmodule{AtteanX::Endpoint} & Gregory Todd Williams &
  \url{kasei/atteanx-endpoint} \\ % 0.001

  \pmodule{RDF::LDF} &  Patrick Hochstenbach, Gregory Todd Williams, Jakob Voß,
  Kjetil Kjernsmo & \url{phochste/RDF-LDF} \\ % 0.17

@@

The Attean framework was born from the experiences the PerlRDF
community gained with \pmodule{RDF::Trine}, the Perl counterpart to
the more well-known Jena framework, and the opportunities presented by
the introduction of traits \cite{traits}, or roles as they are known,
to the Perl world.

Traits are groups of methods that serve as a primitive unit of code
reuse. Traits are not constructed to objects themselves and do not
use inheritance for composition, instead a class is composed by a set of
traits and possibly the class' own methods, and then instantiated. A
trait can also require a set of methods, and as such, is similar to
interfaces, but since its focus is code reuse, it can also provide a
default implementation.
